A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Fix heading
Add Operations intro

\section{Efficient Operations}
\label{sec:efficient-operations}

@@

\begin{figure}[ht]
    \centering
    \includestandalone[height = 3cm]{figs/min-obdd}
    \label{fig:min-obdd}
    \caption{Minimized OBDD (optimal).}
\end{figure}
\tbr

>>>>

\section{Operations}
\label{sec:operations}

Bryant's~\cite{BRYANT86, BRYANT92} main focus was to define algorithms performing
symbolic operations on graphs representing Boolean functions. The most basic
operation is \textit{Apply} which applys a given operation $op$, e.g. \texttt{AND},
to two given functions $f_1$ and $f_2$, and returns the result of $f_1{ }op{ }f_2$.
Another operation is \textit{Restrict}, restricting a given variable $x$ to a
given (constant) value $c$, denoted $f_{x\leftarrow c}$. Furthermore, the
operations \textit{Compose} and \textit{Satisfy} can be defined as graph
algorithms. \tbr

@@

\begin{figure}[ht]
    \centering
    \includestandalone[height = 3cm]{figs/min-obdd}
    \label{fig:min-obdd}
    \caption{Minimized OBDD (optimal).}
\end{figure}
\tbd
